\begin{thebibliography}{50}

\bibitem{Thru2010} S. Thurm and Y. Kane, ‘Your Apps Are Watching You’, The Wall Street Journal, Dec.
2010. http://online.wsj.com/article/SB10001424052748704694004576020083703574602.html, last visited September 2012

\bibitem{Arv2011} Arvind Narayanan, ‘Price Discrimination is All Around You’, http://33bits.org/2011/06/02/price-discrimination-is-
all-around-you/, last visited September 2012.

\bibitem{Nara2011c} Arvind Narayan, ‘The Linkability of Usernames: a Step Toward “Uber-profiles”’, blog posts, Feb.
2011. http://33bits.org/2011/02/16/usernames-linkability-uber-profiles/, last visited September 2012.

\bibitem{Nara2011a} A. Narayanan. ‘There is no such thing as anonymous online tracking, available at: http://cyberlaw.stanford.edu/node/6701, last visited September 2012.

\bibitem{Mull2011a} J. Mullen, ‘Judge approves \$2.4 million Quantcast privacy settlement’, paidContent, available
at: http://paidcontent.org/2011/06/15/419-judge-approves-2-4-million-quantcast-privacy-settlement/, last visited September
2012.

\bibitem{Mull2011b} ‘Second privacy law suit over cookies’ falls apart’, paidContent, available at: http://paidcontent.org/2011/08/19/419-privacy-lawsuits-over-flash-cookies-falling-apart/, last visited September 2012.

\bibitem{FTC2011a} Federal Trade Commission (2011, March) ‘FTC puts an end to tactics of online advertising company that deceived
consumers who wanted to ‘opt out’ from targeted ads’, available at: http://ftc.gov/opa/2011/03/chitika.shtm, last visited
September 2012.

\bibitem{FCT2011b} Federal Trade Commission (2011, November) ‘Online advertiser settles FTC charges ScanScout deceptively used
Flash cookies to track consumers online’, available at: http://www.ftc.gov/opa/2011/11/scanscout.shtm, last visited
September 2012.

\end{thebibliography}
