\section{Prescription}

% It would not make for reasonable or practical regulation to force all application developers to adopt strong privacy measures as many firms make a significant amount of revenue from these sources, likewise, it would not suffice to do nothing and let the current situation stand as it is. 

Care must be taken when approaching the mobile ecosystem through the legislative lens of privacy control. Certainly, draconian measures that would limit application developers from collecting any personal information would be devastating to the industry. Many applications must use this type of data for the legitimate purposes of creating accounts for users and providing other services. On the other hand, the current legal climate of notice and choice is not sufficient in protecting the privacy of consumers in the mobile realm. 
Furthermore, with the lack of consumer awareness, the demand placed on privacy is not a strong enough market force to cause change in the mobile application industry. 
Therefore, policy in conjunction with consumer advocates must step in to better protect consumer privacy on the smartphone. 



% \paragraph{FTC should push vendors to regulate apps}


% NOTE: There is already a norm in place to pay for apps 



	\subsection{Dangers of Explicit Statutes} 

One danger that must be mentioned when addressing any regulation regarding the gathering of smartphone data is the possible societal impacts of limiting the use of such data. Certainly, not all data uses are evil. Many important discoveries and innovations would not have been possible without the unrestricted access to personal data. 

In one case, researchers at Harvard School of Public Health carried out a study in Kenya that consisted of analyzing the location data of nearly 15 million mobile phones to try and understand the infection patterns of malaria\cite{unlock}. The study found that human travel carried the infection more so than travel by mosquitoes, and that the spread of the infection followed stable patterns every year. Ultimately, the study identified areas where malaria treatment centers would be most effective, and infection rates have gone down \%25 since 2000 due targeted prevention. 

Clearly, some uses of mobile data can benefit an entire population, and as such, any policy implemented should not block the legitimate uses of personal, mobile data when the user consents to its use. 
As a result, legislation should emphasize the prevention of harm in the use of personal data and not criminalize the mere ownership of personal data sets as long as they were acquired through legitimate processes. 

%They simply must be extended to the smartphone realm. 

 	\subsection{Technological Solution}
% Talk about how the market can help solve the privacy problem by allowing users to select what applications are allowed to access which data sets
% Like what apple ios is doing right now. 

% Thankfully, Apple has announced that it will be deprecating the use of the UDID in IOS6 due to the privacy concerns. MORE INFO NEEDED HERE

Any regulation that uses specific, technological requirements in its language would become anachronistic rather quickly as technology advances. Thus, any statute attempting to resolve privacy issues specific to smartphones should be avoided. Instead, the FTC can use its influence to push recommendations and best practices onto the mobile ecosystem in order to achieve an industry regulated atmosphere. 

Possibly under threat of creating what is known as a Trade Rule, the FTC could push mobile phone platforms to create better privacy controls for the phones that they run on. 
Since data collection occurs through the operating system of the mobile phone via permissioned access to specific data sets, the operating system is in the best position to block the application of these data. 

Apple's IOS 6 has made great progress in this direction, offering users a privacy control panel. The panel options start with the different types of data that may be collected, location and contacts for example, and upon tapping a specific data type, IOS 6 shows the user all the applications that request access to that data. The user can then, app by app, grant or revoke access to that application's use of the data.
This kind of control is applauded by privacy advocates and models exactly the kind of innovative solutions that only the operating system creators can provide. 
The very existence of this kind of control would allow consumers to be more aware of the data collection practices of certain applications. 

Currently, Android users are only made aware of the types of data that an application will collect when they initially download the application. As mentioned previously, the user typically does not pay attention to these notices nor have a choice other than to be excluded from using the service that the application provides if they disagree with the practices.
With good privacy controls in place however, the mechanism of notice and choice becomes more effective because the user can choose to still use the application, but in a way that retains her privacy preferences.

As the consumer is more easily able to deny applications the data that they request, application will need to make more clear and concise arguments for the use of that data in order to persuade the consumer to grant access to personal data sets. This approach has the extra benefit of making notices more human readable since now the drafting party is creating the notice directly for the consumer and not for a lawyer. 
It follows then, that users will become more aware of the value that their data holds and
thus will be able to make a more informed choice.


 	\subsection{Regulatory Solution}
% This would be more related to the backend of data collection, What uses are appropriate for data collection comapnies,

% Intro 
While this type of technological approach works great to protect consumers against data leakage from specific data sets such as location data, it is inherently limited by the technology that implements it. For instance, any data that the user supplies to the application directly, username, email, date of birth or application usage statistics for example, cannot be blocked by the operating system short of cutting off network usage from the application.
However, if this type of limitation where implemented it would make it extremely difficult for application developers to create useful applications as many applications fundamentally require access to the network. 

Another area that any technological approach could not influence is the process of what happens to personal data after the point of collection. If an application user decides to allow some app access to her location data in order to get directions home, she would be offered no protection against how that data is used in the future. These holes in the solution beg resolution through regulation. 

	% \paragraph{Building on Existing Statutes to Protect Mobile Data}

% Fortunately, there are already in place a number of statutes regarding the security of data sets containing personal data. 

% These problems are also good candidates for regulation because any regulation passed in this light would have benefits that carry through more than just the mobile world. Consider privacy regulation on personal data would to to the online tracking practices of the current day. \hl{this is shit}

	 \paragraph{Suggestions on Policy formation} \ 
	%Something that more resembles the approaches found in many FIPPS 

% Regulation should use existing fair information privacy practices (FIPPS) such as the 

% Intro 
The focus on notice and choice in the United States for dealing with privacy issues in the mobile realm have resulted in a legal climate that emphasizes bureaucratic legislation which places extra costs on consumers and business, instead of encouraging enhanced privacy protection\cite{fair}.
What is required, is a shift in the enforcement strategy undertaken by the FTC to promote the fair use of collected personal information, rather than the current approach of promoting privacy policies and then bringing allegations against companies who offend their policies. 

% Legislation main points (Consumer data bill of rights)
Spelling out the exact components required for effective legislation is beyond the scope of this paper. Fortunately, encouraging work is being done with respect to privacy legislation in what has become known as the Consumer Data Bill of Rights\cite{billofrights}.
In this report, seven privacy principals are detailed pertaining to the commercial use of personal data. 
I will outline the suggestions in that report and try to extend them to cover any issues that may be novel to the smartphone.

% Only deal with personally identifiable information 
Any legislation dealing with data collected through a smart phone should make the distinction between personally identifiable and anonymized data. Here, personally identifiable, would mean any data connected to a name, email address, device unique identifier or any other information that could link the data to a specific person or device. Furthermore, no legislation should be put forth that attempts to regulate the use of anonymous data due to the problematic externalities that would arise from such a practice. Anonymous data is often used for research that is beneficial to society with no harm to the individuals that provide the data\cite{unlock}. Also, by its nature, anonymous data could never be used to collect damages if a company was to violate any legislation surrounding the use of such data since it could not be proven to actually belong to a plaintiff. Therefore, any statute constructed should only deal with personally identifiable information. 

% transparency
Currently, applications do not need to publish a privacy policy, they are only encouraged by the FTC to do so. To improve transparency, policy should be put in place to require any application or service that uses personal data to create a privacy policy and obtain consent from the user before collecting data. To avoid any chilling effect that such regulation may have on startup companies, a clause could be added which excludes any application or service with less than 10,000 users from abiding. 

% security 
To promote the enhancement of privacy protection within the commercial realm, the FTC should be given enforcement grounds to pursue companies who do not adequately secure the personal data that they collect. Statutes could be put in place that create liability for companies whose data sets are compromised in conjunction with appropriate negligence in securing that data. 

% Extended use
Consumers should also be protected against the long term, and unintended uses of their personal data. Any privacy legislation should consider enacting a proper way of allowing consumers to dispose of personal data sets from applications upon the termination of their accounts or services. Given the complexities of the mobile and online advertising ecosystem, it would be incredibly difficult to ensure that all traces of personal data collected through a specific application are appropriately deleted. In light of this fact, the mechanism of notice will need to be sufficient in informing the consumer that any data shared with third parties would not fall under this regulation. 


% 

	\subsection{Notable Current Developments}

Currently, there is some encouraging debates and conversations happening in the legislative sector with regards to mobile privacy. One such development is a bill introduced by representative Hank Johnson called the Application Privacy, Protection, and Security (or APPS) Act. This bill would make notices of privacy procedures mandatory for mobile applications, provide opt-out and deletion measures to consumers, and put in place statutes for the security of any collected personal data\cite{hank}.

Also, the Obama administration has put forth what it is referring to as the Consumer Data Bill of Rights. It contains legislative suggestions to congress which specify the core principals that are common to many other fair information privacy practices\cite{obama}. It will be interesting to see if any privacy legislation materializes out of that report. 
